Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}

### 2016-04-20 paper/paper.tex
Added top words table.

TOPIC TABLE HERE

@@

\subsection{Topic Analysis}

We next want to get a sense of what the content topics look like and whether they correspond to real world events.  See table \ref{tab:content_topics}, for the top 10 words for a subset of six topics that we consider content topics.  These topics correspond to real world politically significant events.  For instances the Libya topic captures information about the Benghazi scandal as well the collapse of Gaddafi's administration.

@@

See table \ref{tab:top_senders} for a ranking of the 14 senders for the subset of content topics explored above.  This table presents the top five senders for each of the topics based on the average topic proportion for each sender.  The sorting that we get back seems to fit with a human understanding of each of the senders, Sidney Blumenthal, who appears to be most associated with the Israel, Election and Obama topics is a long standing advisor to the Clinton family who has written extensively on US politics as well as foreign policy.  Similarly, Huma Abedin, who is most associated with Libya was a key figure during the Benghazi hearings and was generally strongly associated with foreign policy, particularlly in the Middle East while Hillary Clinton's Deputy Chief of Staff.  Finally, Judith McHale, who is most associated with the Afghanistan and international development topic was Under Secretary of State for Public Diplomacy and Public Affairs during the early portion of the email corpus under Hillary.  She also has been strongly associated with a number of philanthropic efforts.  It may be interesting to note that Hillary does not appear to be strongly associated with many of our subset of content topics.  This pattern persists through the remainder of the content topics, in general, Hillary does not appear to send many emails strongly associated with most of the content topics.

>>>>

\begin{table}[htb] \centering \scriptsize
\include{top_words_table}
\caption{Topic Top Words}
\label{tab:top_words}
\end{table}

@@

\subsection{Topic Analysis}
We next want to get a sense of what the content topics look like and whether they correspond to real world events.  See table \ref{tab:content_topics}, for the top 10 words for a subset of six topics that we consider content topics.  These topics correspond to real world politically significant events.  For instances the Libya topic captures information about the Benghazi scandal as well the collapse of Gaddafi's administration.

@@

See Table~\ref{tab:top_senders} for a ranking of the 14 senders for the subset of content topics explored above.  This table presents the top five senders for each of the topics based on the average topic proportion for each sender.  The sorting that we get back seems to fit with a human understanding of each of the senders, Sidney Blumenthal, who appears to be most associated with the Israel, Election and Obama topics is a long standing advisor to the Clinton family who has written extensively on US politics as well as foreign policy.  Similarly, Huma Abedin, who is most associated with Libya was a key figure during the Benghazi hearings and was generally strongly associated with foreign policy, particularlly in the Middle East while Hillary Clinton's Deputy Chief of Staff.  Finally, Judith McHale, who is most associated with the Afghanistan and international development topic was Under Secretary of State for Public Diplomacy and Public Affairs during the early portion of the email corpus under Hillary.  She also has been strongly associated with a number of philanthropic efforts.  It may be interesting to note that Hillary does not appear to be strongly associated with many of our subset of content topics.  This pattern persists through the remainder of the content topics, in general, Hillary does not appear to send many emails strongly associated with most of the content topics.
